Learning Causally-Generated Stationary Time Series

### 2017-02-24 doc/paper.tex
final edits for now

\begin{model}[CGCPM (First Formulation)] \label{mod:cgpcm}
    \begin{align*}
        x &\sim \mathcal{GP}(0,\delta(t-t')), \\
        h &\sim \mathcal{GP}(0, k_h(t,t')), \\
        f\cond h, x &= \sigma_f \int^t h(t- \tau)x(\tau)\id{\tau}.
    \end{align*}
\end{model}
\begin{model}[CGPCM (Second Formulation)] \label{mod:cgpcm2}
    \begin{align*}
        h &\sim \mathcal{GP}(0, k_h(t,t')), \\
        f \cond h &\sim \mathcal{GP}\left(0,  \sigma_f^2\int_0 h(|t-t'|+\tau)h(\tau)\id{\tau} \right).
    \end{align*}
\end{model}

@@

In summary, the CGPCM models differentiable phenomena if $h(0)=0$ and non-differentiable phenoma if $h(0)\neq 0$. In the latter case $|h(0)|$ quantifies the level of roughness.

>>>>

\begin{model}[CGCPM (First Formulation)] \label{mod:cgpcm}
    \begin{align*}
        &x \sim \mathcal{GP}(0,\delta(t-t')), \;
        h \sim \mathcal{GP}(0, k_h(t,t')), \\
        &f\cond h, x = \sigma_f \int^t h(t- \tau)x(\tau)\id{\tau}.
    \end{align*}
\end{model}
\begin{model}[CGPCM (Second Formulation)] \label{mod:cgpcm2}
    \begin{align*}
        h &\sim \mathcal{GP}(0, k_h(t,t')), \\
        f \cond h &\sim \mathcal{GP}\left(0,  \sigma_f^2\int_0 h(|t-t'|+\tau)h(\tau)\id{\tau} \right).
    \end{align*}
\end{model}

@@

In summary, the CGPCM models differentiable phenomena if $h(0)=0$ and non-differentiable phenomena if $h(0)\neq 0$. In the latter case $|h(0)|$ quantifies the level of roughness. Performing inference for the filter will therefore automatically infer the differentiability of the underlying process from possibly noisy data.
